The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-12-02 manuscript/manuscript.qmd
change to my non-student email and correct some typos

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
short-title: "China's ONGO Law and International Civil Society"
date: "2023-11-29"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  TODO: **Update this based on the finished version of the paper.** China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations. In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law. We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas. We argue that the less contentious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in. China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.bib
link-citations: true
---

@@

What factors could have contributed to the contrasting experiences of TNC and Greenpeace under the ONGO Law? After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [TO DO: add citations]. In a public interview with TNC’s RO in China about their registration experience, the chief representative stated TNC’s working approach in China has been “science-based”, using “non-confrontational, collaborative approach in working closely with governments, the business community and others” [@ChinaPhilanthropyReserchInstitute:2018a]. Over the years, they have provided technical support for the central government and local governments like the Yunnan and Zhejiang Province to build national parks and nature reserve areas and helped drafted such documents as the China Biodiversity Conservation Strategy and Action Plan (2011-2030). Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the content of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in relatively large number of provinces. In contrast, Greenpeace states in their mission that they work as “independent campaigning organizations that use peaceful protest and creative confrontation to expose global environmental problems”. Their description of the work in China also uses such key words as “brings change”, “non-violent direct action”, and “impartiality and independence”. One project Greenpeace shares on their website their exposure of the damages the company Sinar Mas Group's did in southwest Yunnan back in 2004. The conducted three rounds of  independent investigation and later revealed that the multinational paper industry company used reforestation as a cover while actually logging Yunnan's natural forests. Although this confrontation was not with the government, it showcases Greenpeace’s investigative, watch dog like work stance. To the authority, it would mean less predictable and manageable.

>>>>

---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
short-title: "China's ONGO Law and International Civil Society"
date: "2023-11-29"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  TODO: **Update this based on the finished version of the paper.** China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations. In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law. We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas. We argue that the less contentious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in. China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.bib
link-citations: true
---

@@

What factors could have contributed to the contrasting experiences of TNC and Greenpeace under the ONGO Law? After analyzing the data, the working approach and relationship with the government emerged as pivotal differences between the two INGOs, which fits existing discussions on the differential treatment of INGOs based on their relationship with the authority [TO DO: add citations]. In a public interview with TNC’s RO in China about their registration experience, the chief representative stated TNC’s working approach in China has been “science-based”, using “non-confrontational, collaborative approach in working closely with governments, the business community and others” [@ChinaPhilanthropyReserchInstitute:2018a]. Over the years, they have provided technical support for the central government and local governments like the Yunnan and Zhejiang Province to build national parks and nature reserve areas and helped drafted such documents as the China Biodiversity Conservation Strategy and Action Plan (2011-2030). Using the non-confrontational working model and establishing long partnerships with the government enabled TNC to secure the consent of a national governmental agency in corresponding issue area to be their PSU, and thus successfully got registered and authorized to operate in a relatively large number of provinces. In contrast, Greenpeace states in their mission that they work as “independent campaigning organizations that use peaceful protest and creative confrontation to expose global environmental problems”. Their description of the work in China also uses such key words as “brings change”, “non-violent direct action”, and “impartiality and independence”. One project Greenpeace shares on their website was the exposure of the damages the company Sinar Mas Group's did in southwest Yunnan back in 2004. They conducted three rounds of  independent investigations and later revealed that the multinational paper industry company used reforestation as a cover while actually logging Yunnan's natural forests. Although this confrontation was not with the government, it showcases Greenpeace’s investigative, watchdog like work stance. To the authority, it would mean less predictable and manageable.
